---
title: "p8105_hw6_rw2844"
author: "Renjie Wei"
date: "11/24/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(cowplot)
library(patchwork)
library(modelr)
library(p8105.datasets)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "100%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
set.seed(2844)
```

# Problem 1





```{r read_homicide}
homicide_df = 
  read_csv("homicide-data/homicide-data.csv", na = c("","NA","Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolved = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1
    )
  ) %>% 
  select(city_state, victim_age, victim_race, victim_sex,resolved) %>% 
  filter(
    victim_race %in% c("White","Black"),
    city_state != "Tulsa, AL")
```


Start with one sample city, Baltimore.
```{r one_city}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolved ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

```{r map_to_cities}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = .x,family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state,term,OR,starts_with("CI"))
```
```{r cities_plot}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>% 
  ggplot(aes(x = city_state, y = OR))+
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


# Problem 2


Read and clean the dataset.
```{r birth_data}
baby_df = 
  read_csv("./data/birthweight.csv") %>% 
  mutate(
    babysex = case_when(babysex == 1~"male", babysex == 2~"female"),
    malform = case_when(malform == 0~"absent", malform == 1 ~ "present")
    ) %>% 
  mutate(
    across(
      .cols = c("frace", "mrace"),
      ~ case_when(
        .x == 1 ~ "White",
        .x == 2 ~ "Black",
        .x == 3 ~ "Asian",
        .x == 4 ~ "Puero Rican",
        .x == 8 ~ "Other",
        .x == 9 ~ "Unknown"
        )
      ),
    across(where(is.character), as.factor)
    ) 

str(baby_df)
# sum(is.na(baby_df)) = 0
```

Build a regression model for birthweight.

Let's try to regress birthweight on 
`babysex`,`blength`,`gaweeks`,`momage`,`parity`,`ppwt`,`wtgain`and `smoken`.


```{r propose_birthweight_reg}
proposal_model = 
  lm(bwt ~ babysex + blength + gaweeks + momage + parity + ppwt + wtgain + smoken, data = baby_df)

proposal_model %>% broom::tidy() %>% knitr::kable(digits = 3)

```

Plot of residuals verses fitted values
```{r proposal_plt}
proposal_plt =
  baby_df %>% 
  add_predictions(proposal_model) %>%
  add_residuals(proposal_model) 

pred_plt1 = 
  proposal_plt %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(aes(size = resid), alpha = .1)

pred_plt2 = 
  proposal_plt %>% 
  ggplot(aes(x = bwt, y = pred)) +
  geom_point(alpha = .1)

pred_plt3 = 
  proposal_plt %>% 
  ggplot(aes(x = resid))+
  geom_density()

plot_grid(pred_plt1,pred_plt2,pred_plt3, ncol = 3)
```

**Comments:**

  + Residuals seems to be larger when the predict value is low.
  
  + The model fits well when birthweigth lies between 2000 grams to 4000 grams.
  
  + The distribution of residuals are approximately normal (with a long tail).
  
  
Let's do the model comparison.

```{r baby_crossvalidation}

baby_cv = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    my_model = map(train,  ~lm(bwt ~ babysex + blength + gaweeks + momage + parity + ppwt + wtgain + smoken, data = .x)),
    simple_model = map(train, ~lm(bwt ~ bhead + gaweeks, data = .x)),
    complex_model = map(train, ~lm(bwt ~ bhead*blength*babysex, data = .x)),
    rmse_my = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
    rmse_simple = map2_dbl(simple_model, test, ~rmse(model = .x, data = .y)),
    rmse_complex = map2_dbl(complex_model, test, ~rmse(model = .x, data = .y))
  )

baby_cv_tidy = 
  baby_cv %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(model = fct_inorder(model))
  

baby_cv_tidy %>% 
  ggplot(aes(x = model, y = rmse, group = model, color = model)) +
  geom_violin(alpha = .3) +
  theme(legend.position = "none") +
  labs(
    title = "RMSE for Three Models",
    x = "Models",
    y = "RMSE"
  )
  
  

my_model = lm(bwt ~ babysex + blength + gaweeks + momage + parity + ppwt + wtgain + smoken, data = baby_df)
simple_model = lm(bwt ~ bhead + gaweeks, data = baby_df)
complex_model = lm(bwt ~ bhead*blength*babysex, data = baby_df)
```

We got the crossvalidation results from above 


# Problem 3

Import the data.
```{r rnoaa_import, include = F , cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r rnoaa_reg}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm",se = F)
```
 
```{r}
weather_boot = 
  weather_df %>% 
  bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy),
    glanced = map(models, broom::glance)
    ) 
